---
title: "data 605 wk5 assignment"
author: "Jun Pan"
date: "March 2, 2019"
output: html_document
---
```{r}
library(MASS)
```


Choose independently two numbers B and C at random from the interval [0, 1] with uniform density. Prove that B and C are proper probability distributions.   Note that the point (B,C) is then chosen at random in the unit square. 
 Find the probability that 
(a) B + C < 1/2. 
```{r}
knitr::opts_chunk$set(echo = TRUE)
B <- runif(1000, min = 0, max = 1)
C <- runif(1000, min = 0, max = 1)

X <- B + C
plot(density(X))
shapiro.test(X)
qqnorm(X)
qqline(X, col = 2)
hist(X)
```
I utalized the shapiro-wilk test and qqplots to show that X is a normal distribution.  Base on the x distribution on the graph, the X < 1/2 is equal to 0.5/2 = 0.125
 
 
(b) BC < 1/2. 
```{r}
Y <- B * C
fit1 <- fitdistr(Y, "exponential")

hist_Y <- hist(Y, freq = FALSE, breaks = 10, xlim = c(0, quantile(Y, 0.99)))
curve(dexp(x, rate = fit1$estimate), col = "red", add = TRUE)

hist_density <- sum(hist_Y$density * .1)
hist_density_0.5 <- sum(hist_Y$density[1:5]*.1)
hist_density_0.5
```
 
 The Y distribution is exponential distribution.  The probability of BC < 1/2 is 0.845
 




(c) |B ??? C| < 1/2. 
 
```{r}
Z <- abs(B-C)
hist(Z)
#Looking the plot, we can estimate the function f(x) = -200x + 200
int.fun <- function(x){-200*x + 200}
Pro_0.5 <- integrate(int.fun, lower = 0, upper = 0.5)
Pro_0.5
```
 Because the cdf of |B-C| between 0 and 1 is given by F(z)=1-(1-z)^2, then by plugging in 1/2 and 0 for z and substracting, we got 0.75.
 


(d) max{B,C} < 1/2. 
Since B and C are normal distribution
$$\\P(max\{B,C\}) = P(B\leqslant\frac{1}{2}) * P(C\leqslant\frac{1}{2})
\\= 0.5 * 0.5
\\= 0.25
$$
 
 



(e) min{B,C} < 1/2. 
 
$$\\P(min\{B,C\}) = 1 - P(max\{B,C\})
\\= 1 - 0.25
\\= 0.75
$$ 
 